hbm_paper_results

### 2024-04-11 paper_lbcc_results.Rmd
study-level means

Deltas

```{r}
deltas_df <- fread(file=paste0(der_path, "/batch.study_pred_deltas.csv"))
# skimr::skim(deltas_df)
cent_deltas_df <- deltas_df %>%
  mutate(study=sub("\\_.*", "", site),
         age_years=age_days/365.25) %>%
  dplyr::select(!contains(".z") & !ends_with("_total") & !contains("TBV")) #drop z-scores and non-centiles

tbl.df <- as.data.frame(table(cent_deltas_df$site, cent_deltas_df$study))
min(gam_centile_df$age_years) == min(cent_deltas_df$age_years)
```

@@

Sample plot
```{r}
#reorder studies by age
age.df <- cent_deltas_df %>%
  group_by(study) %>%
  summarize(mean_age = mean(age_years)) %>%
  arrange(-mean_age)

sample_boxplot <- cent_deltas_df %>%
  mutate(study = factor(study, levels=c(age.df$study), ordered=TRUE)) %>%
ggplot(aes(y=study, x=age_years)) +
  geom_boxplot(outlier.size = 1, outlier.colour=NULL) +
  theme_linedraw(base_size = 11) +
  #guides(y = ggh4x::guide_axis_nested(delim = "&")) +
  theme(axis.title.x=element_blank(), axis.ticks.y = element_blank(), axis.text.x=element_blank()) +
  labs(color="Sex", y = "Study")

#overall sample
full_boxplot <- 
  cent_deltas_df %>%
  mutate(ylab = "  Full \n  Sample") %>%
  ggplot(aes(y=ylab, x=age_years, color=sex)) +
  geom_boxplot(outlier.size = 1, outlier.colour=NULL) +
  theme_linedraw(base_size = 11) +
  # theme(plot.margin = margin(0,0,0,0, 'cm')) +
  # scale_y_discrete(labels=c("1" = "Full Sample")) +
  labs(color="Sex", x = "Age (Years)", y="")

sample_barplot <- cent_deltas_df %>%
  mutate(study = factor(study, levels=c(age.df$study), ordered=TRUE)) %>%
  ggplot() +
  geom_bar(aes( x=..count../tapply(..count.., ..y.. ,sum)[..y..], y=study, fill=sex)) +
  scale_x_continuous(labels = scales::percent) +
  geom_vline(xintercept = .5, color="lightgray", linetype="longdash") +
  theme_linedraw(base_size = 11) +
  theme(axis.ticks.y = element_blank(), axis.text=element_blank(), axis.title=element_blank()) +
  labs(color="Sex")

full_barplot <- 
  cent_deltas_df %>%
  mutate(ylab = "Full Sample") %>%
  ggplot() +
  geom_bar(aes(x=..count../tapply(..count.., ..y.. ,sum)[..y..], y=ylab, fill=sex)) + 
  scale_x_continuous(labels = scales::percent) +
  geom_vline(xintercept = .5, color="lightgray", linetype="longdash") +
  theme_linedraw(base_size = 11) +
  theme(axis.ticks.y = element_blank(), axis.text.y=element_blank(), axis.title.y=element_blank()) +
  labs(color="Sex", x = "Sex")

@@

```{r}
ggplot(deltas_df, aes(x=age_days, y=delta.sGMV, color=sex)) +
  geom_point() +
  geom_smooth()
```

```{r}
cent_deltas_df_long <- cent_deltas_df %>%
  pivot_longer(cols=starts_with("delta."), names_to="pheno", names_prefix = "delta.", values_to = "delta")

cent_deltas_df_long %>%
  ggplot() +
  geom_histogram(aes(x=delta, color=study, fill=study)) +
  theme(legend.position="none")
```

```{r}
delta_n.sex <- cent_deltas_df_long %>%
  mutate(abs.delta = abs(delta)) %>%
  group_by(sex, study) %>%
  summarise(sex_n = n(),
            mean_abs.delta=mean(abs.delta),
            mean_delta=mean(delta),
            mean_age_yrs=mean(age_days)/365.25) #get number males and females in each study

#get study-level stats
delta_summary.df <- cent_deltas_df_long %>%
  mutate(abs.delta = abs(delta)) %>%
  group_by(study) %>%
  summarise(study_mean_abs.delta=mean(abs.delta),
            study_mean_delta=mean(delta),
            study_mean_age=mean(age_days),
            study_mean_age_yrs=mean(age_days)/365.25,
            study_max_abs.delta=max(abs.delta),
            study_n=n()) %>%
  mutate(pheno_cat="all")
```

```{r}
delta_sum.by.sex.df <- full_join(delta_summary.df, delta_n.sex) %>%
  mutate(sex_prop=sex_n/study_n,
         majority = ifelse(sex_prop > .5, 1, 0))

delta_sum.by.sex.df_piv <- delta_sum.by.sex.df %>%
  pivot_wider(id_cols=c(study, study_n, study_mean_age, study_mean_age_yrs, study_mean_delta, study_mean_abs.delta), names_from=sex, values_from=c(sex_n, sex_prop, mean_delta, mean_abs.delta))

#Merge back female prop back into overall site-level stats
to_merge <- delta_sum.by.sex.df_piv %>%
  dplyr::select(study, sex_prop_Female) %>%
  mutate_at(vars(sex_prop_Female), ~replace_na(., 0)) #set prop Female to 0 if no females in study

delta_sum.df_merged <- full_join(delta_summary.df, to_merge)
```

plots!

delta ~ sex-imbalance

```{r}
delta_sum.df_merged %>%
  ggplot(aes(x=sex_prop_Female, y=study_mean_delta)) +
  geom_count(aes(size=study_n)) +
  geom_smooth(method="lm")

delta_sum.by.sex.df %>%
  ggplot(aes(x=sex, y=mean_delta, color=study, fill=study)) +
  geom_count(aes(size=sex_prop), alpha=0.5) +
  geom_line(aes(group=study)) +
  theme(legend.position="none")

delta_sum.by.sex.df %>%
  ggplot(aes(x=sex, y=mean_delta, color=as.factor(majority), fill=as.factor(majority))) +
  geom_count(aes(shape=as.factor(majority), size=sex_prop), alpha=0.5) +
  geom_line(aes(group=study), color="darkgray")

delta_sum.by.sex.df %>%
  ggplot(aes(x=sex_prop, y=mean_abs.delta, color=mean_age_yrs)) +
  geom_count(aes(size=sex_n)) +
  geom_smooth(method="lm") +
  facet_wrap(~sex)

delta_sum.by.sex.df_piv %>%
  ggplot(aes(x=sex_prop_Female, y=study_mean_abs.delta)) +
  geom_count(aes(size=study_n, color=study)) +
  geom_smooth(method="lm")
```

@@

Test to see if centile score is associated with study in either ComBatLS or ComBat-GAM harmonized data.

@@

```{r}
df_gamlss_feat_aov.study$combat <- "gamlss"
df_gam_feat_aov.study$combat <- "gam"

feat_aov.df <- full_join(df_gamlss_feat_aov.study, df_gam_feat_aov.study)

feat_aov.df %>%
  ggplot() +
  geom_point(aes(x=etasq, y=pheno, color=combat, shape=sig_fdr), alpha=0.6) +
  facet_wrap(~pheno_cat, scales="free")
```

@@

#Study-Level Mean Results

ComBatGAM mean centile ~ age

@@

#overall means
gam_centile_site.mean.df <- gam_centile_df.clean_long %>%
  group_by(study) %>%
  summarize(mean_gam_cent=mean(centile),
            median_gam_cent=median(centile)) %>%
  mutate(pheno_cat = "all")

gam_centile_site.mean.df2 <- left_join(gam_centile_site.mean.df, delta_sum.df_merged)

summary(lm(mean_gam_cent ~ study_mean_age, data=gam_centile_site.mean.df2))
summary(lm(mean_gam_cent ~ study_mean_age + sex_prop_Female + study_n, data=gam_centile_site.mean.df2))

summary(lm(median_gam_cent ~ study_mean_age, data=gam_centile_site.mean.df2))
```

```{r}
#mean in global pheno
gam_centile_site.mean.df.glob <- gam_centile_df.clean_long %>%
  dplyr::filter(pheno %in% vol_list_global) %>%
  group_by(study) %>%
  summarize(mean_gam_cent=mean(centile),
            median_gam_cent=median(centile)) %>%
  mutate(pheno_cat = "global_vol")

gam_centile_site.mean.df.glob2 <- left_join(gam_centile_site.mean.df.glob, delta_sum.df_merged, by="study")

summary(lm(mean_gam_cent ~ study_mean_age, data=gam_centile_site.mean.df.glob2))
```

ComBatLS mean centile ~ age
```{r}
gamlss_centile_df.clean_long <- gamlss_centile_df.clean %>%
  pivot_longer(cols=any_of(pheno_list), names_to="pheno", values_to = "centile")

#overall means
gamlss_centile_site.mean.df <- gamlss_centile_df.clean_long %>%
  group_by(study) %>%
  summarize(mean_gamlss_cent=mean(centile),
            median_gamlss_cent=median(centile)) %>%
  mutate(pheno_cat = "all")

gamlss_centile_site.mean.df2 <- left_join(gamlss_centile_site.mean.df, delta_sum.df_merged)

summary(lm(mean_gamlss_cent ~ study_mean_age, data=gamlss_centile_site.mean.df2))
summary(lm(mean_gamlss_cent ~ study_mean_age + sex_prop_Female + study_n, data=gamlss_centile_site.mean.df2))

summary(lm(median_gamlss_cent ~ study_mean_age, data=gamlss_centile_site.mean.df2))
```

@@

```{r}
all_means.df <- full_join(gam_centile_site.mean.df2, gamlss_centile_site.mean.df2)

all_means.df.long <- all_means.df %>%
  pivot_longer(cols=c("mean_gam_cent", "mean_gamlss_cent"), names_to="combat", values_to = "mean_cent") %>%
  mutate(combat=gsub("mean_(.+)_cent", "\\1", combat))

all_means.df.long %>%
  ggplot(aes(x=study_mean_age_yrs, y=mean_cent, color=combat, size=study_n)) +
  geom_point() +
  geom_smooth(method="lm")
```

Significant

```{r}
#mean in global pheno
gamlss_centile_site.mean.df.glob <- gamlss_centile_df.clean_long %>%
  dplyr::filter(pheno %in% vol_list_global) %>%
  group_by(study) %>%
  summarize(mean_gamlss_cent=mean(centile),
            median_gamlss_cent=median(centile)) %>%
  mutate(pheno_cat = "global_vol")

gamlss_centile_site.mean.df.glob2 <- left_join(gamlss_centile_site.mean.df.glob, delta_sum.df_merged, by="study")

summary(lm(mean_gamlss_cent ~ study_mean_age, data=gamlss_centile_site.mean.df.glob2))

summary(lm(mean_gamlss_cent ~ study_mean_age + study_n + sex_prop_Female, data=gamlss_centile_site.mean.df.glob2))
```

```{r}
all_means.df.glob <- full_join(gam_centile_site.mean.df.glob2, gamlss_centile_site.mean.df.glob2)

all_means.df.long.glob <- all_means.df.glob %>%
  pivot_longer(cols=c("mean_gam_cent", "mean_gamlss_cent"), names_to="combat", values_to = "mean_cent") %>%
  mutate(combat=gsub("mean_(.+)_cent", "\\1", combat))

all_means.df.long.glob %>%
  ggplot(aes(x=study_mean_age_yrs, y=mean_cent, color=combat, size=study_n)) +
  geom_point() +
  geom_smooth(method="lm")
```

>>>>

Unharmonized Centiles
```{r}
raw_centile_df <- fread(file=paste0(der_path, "/lifespan-CN-imp-sites-euler-raw_predictions.csv"))
raw_centile_df <- raw_centile_df %>% mutate(study=sub("\\_.*", "", site),
         age_years=age_days/365.25)

dim(raw_centile_df)
min(raw_centile_df$age_years) == min(gamlss_centile_df$age_years)
```

@@

Sample plot
```{r}
#reorder studies by age
age.df <- gamlss_centile_df %>%
  group_by(study) %>%
  summarize(mean_age = mean(age_years)) %>%
  arrange(-mean_age)

sample_boxplot <- gamlss_centile_df %>%
  mutate(study = factor(study, levels=c(age.df$study), ordered=TRUE)) %>%
ggplot(aes(y=study, x=age_years)) +
  geom_boxplot(outlier.size = 1, outlier.colour=NULL) +
  theme_linedraw(base_size = 11) +
  #guides(y = ggh4x::guide_axis_nested(delim = "&")) +
  theme(axis.title.x=element_blank(), axis.ticks.y = element_blank(), axis.text.x=element_blank()) +
  labs(color="Sex", y = "Study")

#overall sample
full_boxplot <- 
  gamlss_centile_df %>%
  mutate(ylab = "  Full \n  Sample") %>%
  ggplot(aes(y=ylab, x=age_years, color=sex)) +
  geom_boxplot(outlier.size = 1, outlier.colour=NULL) +
  theme_linedraw(base_size = 11) +
  # theme(plot.margin = margin(0,0,0,0, 'cm')) +
  # scale_y_discrete(labels=c("1" = "Full Sample")) +
  labs(color="Sex", x = "Age (Years)", y="")

sample_barplot <- gamlss_centile_df %>%
  mutate(study = factor(study, levels=c(age.df$study), ordered=TRUE)) %>%
  ggplot() +
  geom_bar(aes( x=..count../tapply(..count.., ..y.. ,sum)[..y..], y=study, fill=sex)) +
  scale_x_continuous(labels = scales::percent) +
  geom_vline(xintercept = .5, color="lightgray", linetype="longdash") +
  theme_linedraw(base_size = 11) +
  theme(axis.ticks.y = element_blank(), axis.text=element_blank(), axis.title=element_blank()) +
  labs(color="Sex")

full_barplot <- 
  gamlss_centile_df %>%
  mutate(ylab = "Full Sample") %>%
  ggplot() +
  geom_bar(aes(x=..count../tapply(..count.., ..y.. ,sum)[..y..], y=ylab, fill=sex)) + 
  scale_x_continuous(labels = scales::percent) +
  geom_vline(xintercept = .5, color="lightgray", linetype="longdash") +
  theme_linedraw(base_size = 11) +
  theme(axis.ticks.y = element_blank(), axis.text.y=element_blank(), axis.title.y=element_blank()) +
  labs(color="Sex", x = "Sex")

@@

@@

Test to see if centile score is associated with study in either ComBatLS, ComBat-GAM, or non-harmonized data.

## Unharmonized
```{r}
#clean predictions
raw_centile_df.clean <- raw_centile_df %>%
  mutate(study=sub("\\_.*", "", site),
         age_years=age_days/365.25) %>%
  dplyr::select(!contains(".z") & !ends_with("_total") & !contains("TBV")) #drop z-scores and non-centiles

skim(raw_centile_df.clean)
```

```{r}
raw.feat_to_test <- intersect(pheno_list, names(raw_centile_df.clean))
length(raw.feat_to_test)

df_raw_feat_aov <- data.frame()
for(pheno in raw.feat_to_test){
  # print(pheno)
  df <- tidy(aov(raw_centile_df.clean[[pheno]] ~ raw_centile_df.clean[["study"]]))
  df$pheno <- pheno
  df_raw_feat_aov <- rbind(df_raw_feat_aov, df)
}

df_raw_feat_aov.study <- df_raw_feat_aov %>%
  group_by(pheno) %>%
  mutate(etasq = sumsq / sum(sumsq)) %>%
  ungroup() %>%
  dplyr::filter(term != "Residuals") %>%
  dplyr::mutate(p.val_fdr = p.adjust(p.value, method="fdr", n = length(raw.feat_to_test)), #apply fdr correction across all phenos tested
                  sig_fdr = case_when(p.val_fdr < 0.05 ~ TRUE,
                                      p.val_fdr >= 0.05 ~ FALSE))
df_raw_feat_aov.study %>%
  ggplot() +
  geom_bar(aes(y=sig_fdr))

df_raw_feat_aov.study %>%
  ggplot() +
  geom_histogram(aes(x=etasq, fill=sig_fdr), alpha=0.5)

df_raw_feat_aov.study %>%
  dplyr::filter(sig_fdr == TRUE) %>%
  nrow()
```
```{r}
raw_centile_df.mean <- raw_centile_df.clean %>%
  pivot_longer(cols=any_of(pheno_list), names_to="pheno", values_to = "centile") %>%
  group_by(participant) %>%
  summarize(study = unique(study),
            site = unique(site),
            age_days=unique(age_days),
            sex=unique(sex),
            mean_cent=mean(centile))
nrow(raw_centile_df.mean) == n_unique(raw_centile_df.mean$participant)
```

```{r}
raw_centile_df.mean %>%
  ggplot() +
  geom_boxplot(aes(x=reorder(study, age_days), y=mean_cent)) + 
  #geom_boxplot(aes(x=study, y=mean_cent)) +
  theme(axis.text.x = element_text(angle=90, hjust=0.5))

raw_centile_df.mean %>%
  ggplot() +
  geom_point(aes(x=age_days/365.25, y=mean_cent, color=site), alpha=0.5) +
  geom_smooth(aes(x=age_days/365.25, y=mean_cent), method="lm") +
  theme(legend.position = "none") +
  facet_wrap(~study)
```
linear model

```{r}
summary(lm(mean_cent ~ study, data=raw_centile_df.mean))
summary(aov(mean_cent ~ study, data=raw_centile_df.mean))
```
###Z-Scores

```{r}
#clean predictions
raw_z_df.clean <- raw_centile_df %>%
  mutate(study=sub("\\_.*", "", site),
         age_years=age_days/365.25) %>%
  dplyr::select(!any_of(pheno_list) & !ends_with("_total") & !contains("TBV")) #drop z-scores and non-centiles
```

```{r}
raw.feat_to_test.z <- paste0(raw.feat_to_test, ".z")
df_raw_feat_aov.z <- data.frame()
for(pheno in raw.feat_to_test.z){
  # print(pheno)
  df <- tidy(aov(raw_z_df.clean[[pheno]] ~ raw_z_df.clean[["study"]]))
  df$pheno <- pheno
  df_raw_feat_aov.z <- rbind(df_raw_feat_aov.z, df)
}

df_raw_feat_aov.z.study <- df_raw_feat_aov.z %>%
  dplyr::filter(term != "Residuals") %>%
  dplyr::mutate(p.val_fdr = p.adjust(p.value, method="fdr", n = length(raw.feat_to_test.z)), #apply fdr correction across all phenos tested
                  sig_fdr = case_when(p.val_fdr < 0.05 ~ TRUE,
                                      p.val_fdr >= 0.05 ~ FALSE))
df_raw_feat_aov.z.study %>%
  ggplot() +
  geom_bar(aes(y=sig_fdr))

df_raw_feat_aov.z.study %>%
  dplyr::filter(sig_fdr == TRUE) %>%
  nrow()
```

```{r}
raw_z_df.mean <- raw_z_df.clean %>%
  pivot_longer(cols=any_of(pheno_list.z), names_to="pheno", values_to = "z_score") %>%
  group_by(participant) %>%
  summarize(study = unique(study),
            site = unique(site),
            age_days=unique(age_days),
            sex=unique(sex),
            mean_z=mean(z_score))
nrow(raw_z_df.mean) == n_unique(raw_z_df.clean$participant)
```

```{r}
raw_z_df.mean %>%
  ggplot() +
  geom_point(aes(x=age_days/365.25, y=mean_z), alpha=0.5) +
  geom_smooth(aes(x=age_days/365.25, y=mean_z), method="lm") 
# +
#   facet_wrap(~study)
```

```{r}
summary(lm(mean_z ~ study, data=raw_z_df.mean))
summary(aov(mean_z ~ study, data=raw_z_df.mean))
```

@@

@@

##Comparison Plots

compare magnitude of effect size for study (w/in feature anovas) across unharmonized, combat-gam and combatLS centiles

```{r}
df_gamlss_feat_aov.study$combat <- "gamlss"
df_gam_feat_aov.study$combat <- "gam"
df_raw_feat_aov.study$combat <- "raw"

feat_aov.df <- full_join(df_gamlss_feat_aov.study, df_gam_feat_aov.study)
feat_aov.df <- full_join(feat_aov.df, df_raw_feat_aov.study)

feat_aov.df %>%
  ggplot() +
  geom_point(aes(x=etasq, y=pheno, color=combat, shape=sig_fdr), alpha=0.6) +
  facet_wrap(~pheno_cat, scales="free")
```
```{r}
gamlss_centile_df.mean$combat <- "gamlss"
gam_centile_df.mean$combat <- "gam"
raw_centile_df.mean$combat <- "raw"

mean_cents.df <- full_join(gamlss_centile_df.mean, gam_centile_df.mean)
mean_cents.df <- full_join(mean_cents.df, raw_centile_df.mean)

mean_cents.df %>%
  ggplot() +
  geom_boxplot(aes(x=reorder(study, age_days), y=mean_cent)) + 
  #geom_boxplot(aes(x=study, y=mean_cent)) +
  theme(axis.text.x = element_text(angle=90, hjust=0.5)) +
  facet_wrap(~combat)
```

#Study-Level Mean Centiles ~ Study Ages

##Unharmonzied

```{r}
raw_centile_df.clean_long <- raw_centile_df.clean %>%
  pivot_longer(cols=any_of(pheno_list), names_to="pheno", values_to = "centile")

#overall means
raw_centile_site.mean.df <- raw_centile_df.clean_long %>%
  group_by(study) %>%
  summarize(mean_raw_cent=mean(centile),
            median_raw_cent=median(centile),
            mean_age=mean(age_years),
            study_n= n()) %>%
  mutate(pheno_cat = "all")

summary(lm(mean_raw_cent ~ mean_age, data=raw_centile_site.mean.df))
summary(lm(mean_raw_cent ~ mean_age + study_n, data=raw_centile_site.mean.df))
```

## ComBatGAM

@@

#overall means
gam_centile_site.mean.df <- gam_centile_df.clean_long %>%
  group_by(study) %>%
  summarize(mean_gam_cent=mean(centile),
            median_gam_cent=median(centile),
            mean_age=mean(age_years),
            med_age=median(age_years),
            study_n= n()) %>%
  mutate(pheno_cat = "all")

summary(lm(mean_gam_cent ~ mean_age, data=gam_centile_site.mean.df))
summary(lm(median_gam_cent ~ med_age, data=gam_centile_site.mean.df))
summary(lm(mean_gam_cent ~ mean_age + study_n, data=gam_centile_site.mean.df))
```

## ComBatLS

```{r}
gamlss_centile_df.clean_long <- gamlss_centile_df.clean %>%
  pivot_longer(cols=any_of(pheno_list), names_to="pheno", values_to = "centile")

#overall means
gamlss_centile_site.mean.df <- gamlss_centile_df.clean_long %>%
  group_by(study) %>%
  summarize(mean_gamlss_cent=mean(centile),
            median_gamlss_cent=median(centile),
            mean_age=mean(age_years),
            med_age=median(age_years),
            study_n= n()) %>%
  mutate(pheno_cat = "all")

summary(lm(mean_gamlss_cent ~ mean_age, data=gamlss_centile_site.mean.df))
summary(lm(median_gamlss_cent ~ med_age, data=gamlss_centile_site.mean.df))
summary(lm(mean_gamlss_cent ~ mean_age + study_n, data=gamlss_centile_site.mean.df))
```

@@

```{r}
all_means.df <- full_join(gam_centile_site.mean.df, gamlss_centile_site.mean.df)
all_means.df <- full_join(all_means.df, raw_centile_site.mean.df)

all_means.df.long <- all_means.df %>%
  pivot_longer(cols=c("mean_gam_cent", "mean_gamlss_cent", "mean_raw_cent"), names_to="combat", values_to = "mean_cent") %>%
  mutate(combat=gsub("mean_(.+)_cent", "\\1", combat))

all_means.df.long %>%
  ggplot(aes(x=mean_age, y=mean_cent, color=combat)) +
  geom_point(aes(size=study_n)) +
  geom_smooth(method="lm")

all_means.df.long %>%
  ggplot(aes(x=med_age, y=mean_cent, color=combat)) +
  geom_point(aes(size=study_n), alpha=0.6) +
  geom_smooth(method="lm")
```

```{r}
all_medians.df.long <- all_means.df %>%
  pivot_longer(cols=c("median_gam_cent", "median_gamlss_cent", "median_raw_cent"), names_to="combat", values_to = "median_cent") %>%
  mutate(combat=gsub("median_(.+)_cent", "\\1", combat))

all_medians.df.long %>%
  ggplot(aes(x=med_age, y=median_cent, color=combat)) +
  geom_point(aes(size=study_n), alpha=0.6) +
  geom_smooth(method="lm")
```

#Subject-Level Mean Centiles ~ Mean Study Age

```{r}
study_info <- gam_centile_site.mean.df %>%
  dplyr::select(study, mean_age, med_age, study_n)

raw_centile_df.mean2 <- full_join(raw_centile_df.mean, study_info)
summary(lm(mean_cent ~ mean_age, data=raw_centile_df.mean2))

raw_centile_df.mean2 %>%
  ggplot(aes(x=mean_age, y=mean_cent)) +
  geom_point(aes(color=study), alpha=0.7) +
  geom_smooth(method="lm") +
  theme(legend.position="none")
```

```{r}
gam_centile_df.mean2 <- full_join(gam_centile_df.mean, study_info)
summary(lm(mean_cent ~ mean_age, data=gam_centile_df.mean2))

gam_centile_df.mean2 %>%
  ggplot(aes(x=mean_age, y=mean_cent)) +
  geom_point(aes(color=study), alpha=0.7) +
  geom_smooth(method="lm") +
  theme(legend.position="none")
```

```{r}
gamlss_centile_df.mean2 <- full_join(gamlss_centile_df.mean, study_info)
summary(lm(mean_cent ~ mean_age, data=gamlss_centile_df.mean2))

gamlss_centile_df.mean2 %>%
  ggplot(aes(x=mean_age, y=mean_cent)) +
  geom_point(aes(color=study), alpha=0.7) +
  geom_smooth(method="lm") +
  theme(legend.position="none")
```

Plots

```{r}
gamlss_centile_df.mean2$combat <- "gamlss"
gam_centile_df.mean2$combat <- "gam"
raw_centile_df.mean2$combat <- "raw"

all_subj_means.df <- full_join(gamlss_centile_df.mean2, gam_centile_df.mean2)
all_subj_means.df <- full_join(all_subj_means.df, raw_centile_df.mean2)

all_subj_means.df %>%
  ggplot(aes(x=mean_age, y=mean_cent, color=combat)) +
  geom_point(alpha=0.6) +
  geom_smooth(method="lm")

all_subj_means.df %>%
  ggplot(aes(x=mean_age, y=mean_cent, color=combat)) +
  geom_point(alpha=0.3) +
  geom_smooth(method="lm") +
  facet_wrap(~combat)

summary(lm(mean_cent ~ mean_age, data=raw_centile_df.mean2))
summary(lm(mean_cent ~ mean_age, data=gam_centile_df.mean2))
summary(lm(mean_cent ~ mean_age, data=gamlss_centile_df.mean2))
```

```{r}
summary(lm(mean_cent ~ study_n, data=raw_centile_df.mean2))
summary(lm(mean_cent ~ study_n, data=gam_centile_df.mean2))
summary(lm(mean_cent ~ study_n, data=gamlss_centile_df.mean2))

all_subj_means.df %>%
  ggplot(aes(x=study_n, y=mean_cent, color=combat)) +
  geom_point(alpha=0.6) +
  geom_smooth(method="lm")
```
